---
title: "Extracting Tweets from Twitter API"
author: "Sumit Kant"
date: "27 April 2017"
output: 
  html_document:
    css: theme.css
---
  
# 1. Introduction
  
This is short guide to extract tweets from Twitter API using R. I will be using "lego batman movie" as the search term here. The extracted tweets can used to text mining and Sentiment Analysis which is done in a later post. 

Before extracting the tweets you must have a twitter account.

# 2. Extracting Tweets from Twitter API



## Step 1: Load require Libraries
```{r message=FALSE}
library(twitteR)
library(ROAuth)
library(httr)
```
## Step 2: Set API Keys
```{r warning=FALSE}
consumerKey <- "G8iPPnWlNsSJpbHMHAb0JLoHh"
consumerSecret <- "w3KTC2TSBRKw9CShDeoWThFh96EBrH633X7j7zToNWtulaqhjV"
accessKey <- "449531980-uoNSdT1P5xgmeZfIyhrKjRvxyiFV7yBvJ0RqbWpZ"
accessSecret <- "BQOMQGbzUQmJi1q7pgZphIbF7MkHhqiwQTp9r7BmdJWLq"

# Setting up access for the session
setup_twitter_oauth(consumerKey,consumerSecret,accessKey,accessSecret)
```
## step 3: Grabbing Latest Tweets

```{r warning=FALSE}
search.string = "#legobatmanmovie"
tweets<-searchTwitter(search.string, 500, lang ="en")
```
## Step 4: Saving as .csv file
```{r}
# Saving tweetts in a csv file
setwd('D:/Data Analyst/Own Data/Sentiment Analysis Batman Lego Movie/')
name<-file(description="batmanLegotweets.csv",open="w")
write.csv(twListToDF(tweets),file=name)
close(con = name)
```

