---
title: "Sentiment Analysis for Lego Batman Movie"
author: "Sumit Kant"
date: "27 April 2017"
output: 
  html_document:
    css: theme.css
---

# 1. Introduction

THe Lego Batman Movie is a 3D computer-animated superhero comdey film released in 2017.
The Facebook page of the movie has 430,000+ followers and almost same numbers are talking about this. The movie was released in 17 February in India. The tweets for the sentiment analysis will be taken from 18th Feb.

# 2. Extracting Tweets from Twitter API

## Step 1: Load require Libraries
```{r message=FALSE}
library(twitteR)
library(ROAuth)
library(httr)
```
## Step 2: Set API Keys
```{r warning=FALSE}
consumerKey <- "G8iPPnWlNsSJpbHMHAb0JLoHh"
consumerSecret <- "w3KTC2TSBRKw9CShDeoWThFh96EBrH633X7j7zToNWtulaqhjV"
accessKey <- "449531980-uoNSdT1P5xgmeZfIyhrKjRvxyiFV7yBvJ0RqbWpZ"
accessSecret <- "BQOMQGbzUQmJi1q7pgZphIbF7MkHhqiwQTp9r7BmdJWLq"

# Setting up access for the session
setup_twitter_oauth(consumerKey,consumerSecret,accessKey,accessSecret)
```
## step 3: Grabbing Latest Tweets and saving as text file

```{r warning=FALSE}
search.string = "lego batman movie"
tweets<-searchTwitter(search.string, 3000, lang ="en")

# Saving tweetts in a csv file
setwd('D:/Data Analyst/Own Data/Sentiment Analysis Batman Lego Movie/')
name<-file(description="tweets.csv",open="w")
write.csv(twListToDF(tweets),file=name)
close(con = name)
```
# 3. Conducting Analysis using 'tm' package

### Step 1: Load required libraries
```{r eval=FALSE, message =FALSE}
#loading libraries
library('stringr')
library('readr')
library('wordcloud')
library('tm')
library('SnowballC')
library('RWeka')
library('RSentiment')
library(DT)
library(ggplot2)
library(readr)

# load data
lbm = read_csv("tweets.csv")
windowsFonts(Lato.Regular = windowsFont('Lato Regular'))
```

### Step 2: Preprocessing Data

```{r warning=FALSE}
#extracting relevant data
r1 = as.character(lbm$text)

#Data Preprocessing
sample = sample(r1, (length(r1)))
corpus = Corpus(VectorSource(list(sample)))
corpus = tm_map(corpus, removePunctuation)
corpus = tm_map(corpus, content_transformer(tolower))
corpus = tm_map(corpus, removeNumbers)
corpus = tm_map(corpus, stripWhitespace)
corpus = tm_map(corpus, removeWords, stopwords('english'))
corpus = tm_map(corpus, stemDocument)
dtm_up = DocumentTermMatrix(VCorpus(VectorSource(corpus[[1]]$content)))
freq_up <- colSums(as.matrix(dtm_up))
```
### Step 3: Sentiment
```{r warning=FALSE}
#Calculating Sentiments - Approach 1
sentiments_up = calculate_sentiment(names(freq_up))
sentiments_up = cbind(sentiments_up, as.data.frame(freq_up))
sent_pos_up = sentiments_up[sentiments_up$sentiment == 'Positive',]
sent_neg_up = sentiments_up[sentiments_up$sentiment == 'Negative',]
```
## Positive Sentiments
```{r warning=FALSE}
ggplot(aes(x = freq_up, y = text, label = freq_up, color=freq_up), 
       data = sent_pos_up[sent_pos_up$freq_up>5,]) + 
  geom_point(size=4) +
  geom_text(size=3, position = position_nudge(x = 4), family = "Lato.Regular") +
  theme_gray(base_family = "Lato.Regular") +
  ylab("Positive Sentiments") +
  xlab("Frequencies")
ggsave(filename = "Positive sentiments with Freq more than 5.jpeg", width = 7, height = 4)
```
### Creating WordCloud of Positive sentiments
```{r warning=FALSE}
## Wordcloud positive sentiments
layout(matrix(c(1, 2), nrow=2), heights=c(1, 4))
par(mar=rep(0, 4))
plot.new()
wordcloud(sent_pos_up$text,sent_pos_up$freq,min.freq=5,colors=brewer.pal(6,"Dark2"))
ggsave(filename = "Positive sentiments wordcloud.jpeg", width = 7, height = 4)

```


## Negative Sentiments
```{r warning=FALSE}

## Negative Sentiments
ggplot(aes(x = freq_up, y = text, label = freq_up, color=freq_up), 
       data = sent_neg_up[sent_neg_up$freq_up>5,]) + 
  geom_point(size=4) +
  geom_text(size=3, position = position_nudge(x = 4), family = "Lato.Regular") +
  theme_gray(base_family = "Lato.Regular") +
  ylab("Negative Sentiments") +
  xlab("Frequencies")
ggsave(filename = "Negative sentiments with Freq more than 5.jpeg", width = 7, height = 4)

```
### Creating WordCloud of Negative sentiments
```{r warning=FALSE}
## Wordcloud negative sentiments
layout(matrix(c(1, 2), nrow=2), heights=c(1, 4))
par(mar=rep(0, 4))
plot.new()
set.seed(100)
wordcloud(sent_neg_up$text,sent_neg_up$freq, min.freq=5,colors=brewer.pal(6 ,"Dark2"))
```

